### 2019-06-12 doc/chapters/towards_verifying_addition.tex
more explnation

This is a missing feature in Stainless.
It does not support upper type bound on the class itself.
To track this, there is the \href{https://github.com/epfl-lara/stainless/issues/519}{issue \mypound519} on GitHub.
\begin{lstlisting}[language=scala]
  sealed abstract class Number[T <: Number[T]] extends BasicArithmetic[T]  
\end{lstlisting}

For the sake of convenience we make this a concrete type by replacing T with Int64.

>>>>

This is a missing feature in Stainless.
It does not support upper type bound on the class itself.
To track this, \href{https://github.com/epfl-lara/stainless/issues/519}{issue \mypound519} was created on GitHub during this work.
\begin{lstlisting}[language=scala]
  sealed abstract class Number[T <: Number[T]] extends BasicArithmetic[T]  
\end{lstlisting}

For the sake of convenience we make this a concrete type by replacing T with Int64.
Int64,  because Satoshis uses only Int64.
There are other number typs like UInt16 but for our property we don't need them.
